%-----       letter       ---------------------------------------------------------
% recipient data
\thispagestyle{empty}
\recipient{PartyName}{}
%\today
\opening{Dear Sir or Madam,}
\closing{Sincerely,}
\enclosure[Attached]{curriculum vitae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I read the opportunity description for \$Role with great interest and would like to learn more about it.
To give you a brief overview of my skill set - I have been with CipherTrace for almost 1 year as a Sr DevSecOps engineer, maintaining hundreds of AWS servers, migrating instance to containers, and deploying to ECS, EKS, and GKE.  Prior to that, I was at Questis for almost 3 years and was in charge of Operations and Security for all systems as the Director of IT Operations and DevOps Lead for over 2 years.

I have migrated dozens of applications from on-premise to AWS, designed multiple system architectures for several DoD and commercial projects, contributed to multiple open-source projects, and volunteer at multiple security conferences every year. 

I currently hold multiple Amazon Web Services (AWS) certifications as well as a Certified Information Systems Security Professional (CISSP) certification.  Prior to CipherTrace, I have worked for several government agencies as well as commercial companies and have over 17 years of industry experience spanning security, engineering, operations, networking, and cryptography.  In the past I have held fully remote positions and understand the self discipline required to do so.
As you know, a resume is only a brief list of accomplishments so if the position is still available, I would like to discuss it further.

\makeletterclosing
\clearpage
%-----       resume       ---------------------------------------------------------
\setcounter{page}{1}